---
title: "Title Arial 28pt Bold"
subtitle: "Subtitle Arial (12pt or 28pt) Bold"
author: "Author: Arial 12pt Bold"
date: "Date:  Month YYYY: Arial 12pt Bold"
output:
  word_document:
    reference_docx: \\deqhq1\WQNPS\NPS_Annual_Reports\2017\Basin_Reports_2017\DEQ_word_gen_template.docx
    fig_caption: yes
    toc: yes
  html_document:
    df_print: paged
    toc: yes
---
```{r setup, echo=FALSE, include=FALSE}
require(knitr)

knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning=FALSE,
                      error = FALSE,
                      cache = FALSE,
                      cache.comments = FALSE,
                      include = TRUE,
                      autodep = TRUE,
                      fig.align = "center",
                      eval=TRUE)

require(captioner)

tbls  <- captioner(prefix="Table A-", auto_space = FALSE)
figs <- captioner(prefix="Figure A-", auto_space = FALSE)

```

------

Name: Title
Style type: Paragraph
Style based on: Normal
Style for following paragraph: Body Text

Arial, 28 pt, Bold, Font color: Black
Alignment: Left, Single Spacing

Paragraph:
Indentation Left: 0"
Indentation Right: 0"
Spacing Before:  24 pt
Spacing After:  12 pt
Line Spacing: Single

------

Name: Subtitle,  Author, Date
Style type: Paragraph
Style based on: Title
Style for following paragraph: Body Text

Arial, 12 pt, Bold, Font color: Black
Alignment: Left, Single Spacing

Paragraph:
Indentation Left: 0"
Indentation Right: 0"
Spacing Before:  0 pt
Spacing After:  6 pt
Line Spacing: Single

------

# Header 1 Style

Name: Header 1
Style type: Paragraph
Style based on: Normal
Style for following paragraph: First Paragraph

Arial, 28 pt, Bold, Font color: Black
Alignment: Left, Single Spacing

Paragraph:
Indentation Left: 0"
Indentation Right: 0"
Spacing Before:  24 pt
Spacing After:  6 pt
Line Spacing: Single

## Header 2 Style

Name: Header 2
Style type: Paragraph
Style based on: Normal
Style for following paragraph: First Paragraph

Arial, 18 pt, Bold, Font color: Black
Alignment: Left, Single Spacing

Paragraph:
Indentation Left: 0"
Indentation Right: 0"
Spacing Before:  12 pt
Spacing After:  6 pt
Line Spacing: Single

### Header 3 Style

Name: Header 3
Style type: Paragraph
Style based on: Normal
Style for following paragraph: First Paragraph

Arial, 11 pt, Bold, Font color: Black
Alignment: Left, Single Spacing

Paragraph:
Indentation Left: 0"
Indentation Right: 0"
Spacing Before:  12 pt
Spacing After:  6 pt
Line Spacing: Single

#### Header 4 Style

Name: Header 4
Style type: Paragraph
Style based on: Normal
Style for following paragraph: First Paragraph

Arial, 11 pt, Bold, Font color: Black
Alignment: Left, Single Spacing

Paragraph:
Indentation Left: 0"
Indentation Right: 0"
Spacing Before:  12 pt
Spacing After:  6 pt
Line Spacing: Single

##### Header 5 Style

Name: Header 5
Style type: Paragraph
Style based on: Normal
Style for following paragraph: First Paragraph

Arial, 11 pt, Font color: Black
Alignment: Left, Single Spacing

Paragraph:
Indentation Left: 0"
Indentation Right: 0"
Spacing Before:  6 pt
Spacing After:  6 pt
Line Spacing: Single

###### Header 6 Style

Name: Header 6
Style type: Paragraph
Style based on: Normal
Style for following paragraph: First Paragraph

Arial, 11 pt, Italic, Font color: Black
Alignment: Left, Single Spacing

Paragraph:
Indentation Left: 0"
Indentation Right: 0"
Spacing Before:  6 pt
Spacing After:  6 pt
Line Spacing: Single

# Other Text Styles

## Normal or Body Text Style

Name: Normal or Body Text
Style type: Paragraph
Style based on: Normal
Style for following paragraph: List Bullet

Time New Roman, 11 pt, Font color: Black
Alignment: Left, Single Spacing

Paragraph:
Indentation Left: 0"
Indentation Right: 0"
Spacing Before: 0 pt
Spacing After:  12 pt
Line Spacing: Single


## List Bullet Style

Name: List Bullet
Style type: Paragraph
Style based on: Normal
Style for following paragraph: List Bullet

Time New Roman, 11 pt, Font color: Black
Alignment: Left, Single Spacing

Paragraph:
Indentation Left: 0"
Indentation Right: 0"
Spacing Before: 0 pt
Spacing After:  12 pt
Line Spacing: Single

These are some bullets in 'List Bullet' Style:


* One bullet
* Two bullets
* Three bullets


## Captions

```{r fig-1, fig.cap=figs(name="fig_1", caption= "Caption Arial, 9pt, Bold Color: Black")} 
library(ggplot2)

p1 <- ggplot(iris, aes(Petal.Width, Petal.Length, color=Species)) + geom_point()

p1

```


For figure captions see `r figs('fig_1', display = 'cite')`.

Name: Figure, Captioned Figure, or Caption
Style type: Paragraph
Style based on: Figure
Style for following paragraph: Captioned Figure 

Arial, 10 pt, Bold color: Black
Alignment: Left, Single Spacing

Paragraph:
Indentation Left: 0"
Indentation Right: 0"
Spacing Before: 0 pt
Spacing After:  12 pt
Line Spacing: Single


```{r tbl-1, results="asis"}

knitr::kable(head(iris), padding = 2, digits = 1, caption=tbls(name="tbl_1", caption="table caption 1"))


```


For table captions, see `r tbls('tbl_1', display = 'cite')`.

Name: Figure, Captioned Table, or Caption
Style type: Paragraph
Style based on: Figure
Style for following paragraph: Captioned Figure

Arial, 10 pt, Bold color: Black
Alignment: Left, Single Spacing

Paragraph:
Indentation Left: 0"
Indentation Right: 0"
Spacing Before: 12 pt
Spacing After:  0 pt
Line Spacing: Single


